The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-10-04 article.tex
Updates from ShareLaTeX

{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\gio{@richel: A) I am throwing down some main points to follow to develop a convincing story that follows a clear logic. It might happen that some of these points are repeated and/or in the wrong order. We need to check that.}
\gio{@richel: B) According to my fine graining approach we should at each step deepen every small section. At a certain level I think we can start to re-coarse-grain what we wrote to create the abstract.}

@@

\item The (constant-rate) birth-death (BD) model embodies the common assumption that 
only a single speciation event can occur at any given time.
The MBD model relaxes this assumption, allowing events in which 
large-scale environmental changes lead to a great number of species 
in relatively short time intervals. Such hypothesis can be useful to describe, for example, 
systems like cichlid fish diversification in the 
African Great Lakes: Malawi, Tanganyika and Victoria (\cite{janzen2016}, \cite{janzen2017}).

\item In the MBD model, parameters $\lambda$ and $\mu$ correspond, respectively, 
to the usual per-species speciation and extinction rates. 
Additionally, $\nu$ is the rate at which an environmental change is triggered.
When such event is triggered, all species present in the phylogeny at that moment
have a probability $q$ to speciate (independent on $\lambda$).
The number of species that speciate due to this can also be zero.

>>>>

{\bf Keywords:} computational biology, evolution, phylogenetics, Bayesian analysis, tree prior
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\gio{@richel: A) I am throwing down some main points to follow to develop a convincing story that follows a clear logic. It might happen that some of these points are repeated and/or in the wrong order. We need to check that.}
\gio{@richel: B) According to my fine graining approach we should at each step deepen every small section. At a certain level I think we can start to re-coarse-grain what we wrote to create the abstract.}
\richel{I enjoy this approach! And I know Rampal does not :-)}
\richel{Have you already looked up for a target journal? I know how a journal's constraints have helped me 
in writing an article}

@@

\item The (constant-rate) birth-death (BD) model embodies the common assumption that 
only a single speciation event can occur at any given time.
The Multiple-Birth-Death (MBD) model \richel{I feel MBSD (Multiple Birth Single Death) may be a better name: extinctions are still one at a time} relaxes this assumption, allowing events in which 
large-scale environmental changes lead to a great number of species 
in relatively short time intervals. Such hypothesis can be useful to describe, for example, 
systems like cichlid fish diversification in the 
African Great Lakes: Malawi, Tanganyika and Victoria (\cite{janzen2016}, \cite{janzen2017}).

\item In the MBD model, parameters $\lambda$ and $\mu$ correspond, respectively, 
to the usual per-species speciation and extinction rates. 
Additionally, $\nu$ is the rate at which an environmental change is triggered.
When such event is triggered, all species present in the phylogeny at that moment
have a probability $q$ to speciate (independent on $\lambda$).
The number of species that speciate due to this can also be zero .
